Truthfulness Verification System

### 2011-03-30 trunk/proposal/paper.tex
Some more cosmetic changes

Contrary to our prior report, Wikipedia does have a very rich API, which the wiki software, Mediawiki provides. Of the various features that this API provides there are two searching mechanisms.

@@

[

    * "Forrest Gump"
    *
      -
      [
          o "Forrest Gump"
          o "Forrest Gump (character)"
          o "Forrest Gump (novel)"
          o "Forrest Gump (soundtrack)"
          o "Forrest Gump – Original Motion Picture Score"
          o "Forrest Gump (disambiguation)"
      ]

]

@@

@@

                        if snippet_tokens.intersection(doubt_unit_tokens):
                                print "S",';',title_weight,';',snippet_weight,';',overall_result_weight
                                found = True
                        if title_tokens.intersection(doubt_unit_tokens):
                                print "T",';',title_weight,';',snippet_weight,';',overall_result_weight
                                found = True

@@

Following are a few high priority bugs we are working on

\begin{itemize}
\item Better matching: We tried two ways to match the DU-s in the reutrened results, one a conservative approach that would try to tokenize so that abbreviations like "U.S.A" and monetary amounts like "\$23.00" are kept as tokens. In the more relaxed approach the tokens were all lowercased and split by spaces. This obviously is the most crucial part of the entire process and it appears we should have separate strategy based on the data type of the doubt unit.
\item Building the classifier: We got the data from TREC 9, which is in a question answer format and have finished coverting 100 of the 711 sentences all to statement form with correct answers. Once we have some more sentences labeled we will use it to train a classifier from the features extracted above.
\end{itemize}

\subsubsection{Use of answer.com}
We found that answer.com also contains the correct answers to the for the doubt sentences in almost of all the cases. The precise Q\&A format of closely matching the sentences excites us about the possibilites of using the above mentioned strategies for this site. A lot of domain specific sites (like stackexchange.com, quora.com) have become very popular since 2009, which deviate from the traditional forums in the sense that the user generated content is voted, summarised and exposed to a programmatic interface.

{\em Feb 23 to Mar 9} 
\begin{itemize}
\item Formulated the procedure of truthfulness verification in a more structured way
\item As a result of the procedure formulation, the sections Step-by-step Algorithm for Truthfulness and Verification Examples of Truthfulness Verification are written in a complete revised way compared to the proposal
\item Apart from getting out feet wet with the MQL api, the daunting task is to develop generalized framework that is flexible enough to fit the wide variety of sentences into the rigid structure of Freebase. The learning cure is steep, given the richness and massive size of documentation. Though we are groping in dark currently, we are hopeful that the pieces of the puzzle with soon fit in.
\item Looked into applicability of POS tagger in the context of our problem and found it useful for constructing freebase queries
\item Got some initial promising results by exploring different options such as Wikipedia, answer.com beyond Freebase ontologies. 
\item Worked on porting of existing T-verifier code to linux. The original T-verifier code is for windows only and not generic enough at this moment. We also contacted with the student author about the problems we are facing to port the code to linux. We hope to resolve it soon.
\end{itemize}

{\em Mar 9 to Mar 29} 
\begin{itemize}
\item 
\end{itemize}
\section{Conclusion}
It this paper, we described current system for truthfulness verification of statements found in the web called T-Verifier and described the possible improvements to the current system. We will primarily use authentic information sources such as Wikipedia and Ontologies extracted from Wikipedia such as FreeBase, DBPedia, and YOGA to found the truthfulness of doubtful statements.

>>>>

\label{March9to29}
Contrary to our prior report, Wikipedia does have a very rich API, which the wiki software, Mediawiki provides. Of the various features that this API provides there are two searching mechanisms.

@@

\begin{lstlisting}[label=Opensearch Protocol, caption=Result using Opensearch]
[
    * "Forrest Gump"
      [
          o "Forrest Gump"
          o "Forrest Gump (character)"
          o "Forrest Gump (novel)"
          o "Forrest Gump (soundtrack)"
          o "Forrest Gump – Original Motion Picture Score"
          o "Forrest Gump (disambiguation)"
      ]
]

@@

\begin{lstlisting}[label=pseudo-code,caption=Feature extraction initial steps]

@@

#If the match is found in the snippet
if snippet_tokens.intersection(doubt_unit_tokens):
        print "S",';',title_weight,';',snippet_weight,';',overall_result_weight
        found = True

#if the match is found in the Title
if title_tokens.intersection(doubt_unit_tokens):
        print "T",';',title_weight,';',snippet_weight,';',overall_result_weight
        found = True

#If no match is found
if title_tokens.intersection(doubt_unit_tokens):
        print "N",';',title_weight,';',snippet_weight,';',overall_result_weight
        found = True

@@

The following are the immediate concerns 
\begin{itemize}
\item Better matching: We tried two ways to match the DU-s in the returned results, one a conservative approach that would try to tokenize so that abbreviations like "U.S.A" and monetary amounts like "\$23.00" are kept as tokens. In the more relaxed approach the tokens were all lowercased and split by spaces. This obviously is the most crucial part of the entire process and it appears we should have separate strategy based on the data type of the doubt unit.
\item Building the classifier: We got the data from TREC 9, which is in a question answer format and have finished converting 100 of the 711 sentences all to statement form with correct answers. Once we have some more sentences labeled we will use it to train a classifier from the features extracted above.
\end{itemize}

\subsubsection{Data Description}
The attached file shows the data collected for each sentence from wikipedia. We take the top 10 results returned by searching wikipeida, and calculate the values mentioned above. "S" denotes that $DU$ appears in the snippet, "T", shows that it appears in the Title, and "N" means the $DU$ was not found anywhere. The other values are separated by ';' are title weight,snippet weight,overall result weight.

\subsubsection{Use of answer.com}
We found that answer.com also contains the correct answers to the for the doubt sentences in almost of all the cases. The precise Q\&A format of closely matching the sentences excites us about the possibilities of using the above mentioned strategies for this site. A lot of domain specific sites (like stackexchange.com, quora.com) have become very popular since 2009, which deviate from the traditional forums in the sense that the user generated content is voted, summarised and exposed to a programmatic interface.

\begin{itemize}
\item 
\end{itemize}
\section{Conclusion}
It this paper, we described current system for truthfulness verification of statements found in the web called T-Verifier and described the possible improvements to the current system. We will primarily use authentic information sources such as Wikipedia and Ontologies extracted from Wikipedia such as FreeBase, DBPedia, and YOGA to found the truthfulness of doubtful statements.
